Measurement of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross Sections using a DD Neutron Generator for Medical Isotope Studies

### 2017-04-26 First_np_Paper/first_np_paper.tex
Added keywords to abstract, for Elsevier submission. Final version.
Final version, with cover letter, as submitted for publication review.

% \begin{keyword}
%% keywords here, in the form: keyword \sep keyword

@@

% \end{keyword}

@@

With the exception of decay constants  and time measurement, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries am uncertainty.
Based on the assumption that these uncertainties are uncorrelated, the total relative statistical uncertainty $\delta_\sigma$ is calculated by taking the quadrature sum of the relative uncertainties of each parameter  $\delta_i$:

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Results of cross section measurement. Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
\label{tab:xs_results}
\begin{tabular}{@{}cc@{}}
\toprule
Reaction                                                                            & $\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)                                                                       \\ \midrule
\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} &  \begin{tabular}[c]{@{}c@{}}49.9 $\pm$ 3.2, \\ 49.2 $\pm$ 2.7, \\ 49.0 $\pm$ 2.5\end{tabular} \\  \\[0.1ex]  
\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.9 $\pm$ 2.6, \\ 46.5 $\pm$ 1.7, \\ 46.8 $\pm$ 3.2\end{tabular}  \\ \\[0.1ex]    
\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.9 $\pm$ 1.2, \\ 26.7 $\pm$ 1.4*\end{tabular}                   \\ \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
DD neutron generator \sep Medical Isotope Production \sep Scandium (Sc) and Copper (Cu) radioisotopes \sep Indium \sep Ratio activation \sep Theranostics

@@

\end{keyword}

@@

With the exception of decay constants  and time measurement, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries an uncertainty.
Based on the assumption that these uncertainties are uncorrelated, the total relative statistical uncertainty $\delta_\sigma$ is calculated by taking the quadrature sum of the relative uncertainties of each parameter  $\delta_i$:

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \begin{table}
% \centering
% \caption{Results of cross section measurement. Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
% \label{tab:xs_results}
% \begin{tabular}{@{}cc@{}}
% \toprule
% Reaction                                                                            & $\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)                                                                       \\ \midrule
% \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} &  \begin{tabular}[c]{@{}c@{}}49.9 $\pm$ 3.2, \\ 49.2 $\pm$ 2.7, \\ 49.0 $\pm$ 2.5\end{tabular} \\  \\[0.1ex]  
% \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.9 $\pm$ 2.6, \\ 46.5 $\pm$ 1.7, \\ 46.8 $\pm$ 3.2\end{tabular}  \\ \\[0.1ex]    
% \begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.9 $\pm$ 1.2, \\ 26.7 $\pm$ 1.4*\end{tabular}                   \\ \bottomrule
% \end{tabular}
% \end{table}
\begin{table}
\centering
\caption{Results of cross section measurement. Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
\label{tab:xs_results}
\begin{tabular}{@{}cS[table-format=+2.1,
                  table-figures-uncertainty=1]@{}}
\toprule
Reaction                   & \multirow{1}*{\minitab[c]{$\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)}}       \\ \midrule
\multirow{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})}} & 49.9 \pm 3.2 \\ 
											& 49.2 \pm 2.7 \\ 
											& 49.0 \pm 2.5 \\  \\[0.1ex]  
\multirow{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})}} & 45.9 \pm 2.6 \\ 
											& 46.5 \pm 1.7 \\ 
											& 46.8 \pm 3.2  \\ \\[0.1ex]    
\multirow{2}*{\minitab[c]{\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})}} & 25.9 \pm 1.2 \\ 
											& 26.7 \pm 1.4*                   \\ \bottomrule
\end{tabular}
\end{table}
